---
title: "ESM206_Lab10"
author: "Ali Martin"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
library(usethis)

library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
```

## beepr::beep()

Use `beep()` to give yourself an audio alert

## Write a for loop + beep

write a reverse `rev()`sequence to countdown from 99 to 1

```{r, eval = FALSE}
for (i in rev(seq(1:9999))) {
  print(paste(i, 'bottles of beer on the wall'))
}

beep(4)
```

## Praise is nice


```{r}
praise("${EXCLAMATION}!!!!! This code works ${adverb_manner}!") #create a randomly selected term using ${}

praise ("Holy ${creating}, Batman - this code works ${ADVERB_MANNER}!!")
```

## cowsay:: say to have characters say something

```{r}
say("I love tacos!" , by = "hypnotoad")
```

## usethis for everything 

R Project first, then git and GitHub repo.

-usethis:: use_git() to make version controlled local repo
-usethis:: use_github() to create upstream repo

## paletteer: aggregated color palettes

-use view(palettes_d_names) to get list of palettes

```{r}
storms %>% 
  group_by(name) %>% 
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>% 
  slice_min(n = 10, min_pressure) %>% 
  ggplot(aes(x = min_pressure, y = name)) +
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("palettetown::latias") # insert "pkg::palette" pkg is pkg name
```

## Make a map of Jornada LTER Vegetation

```{r}
jornada_veg <- read_sf("doc.kml") %>% 
  select(Name)%>% 
  clean_names()

ggplot() + 
  geom_sf(data = jornada_veg, color = name) +
  scale_fill_paletteer_c()

# Update this map:
# Each vegetation type has a different fill color
# Update theme
# Customize color palette
```

